Neural Models for Target-Based Computer-Assisted Musical Orchestration: A Preliminary Study

### 2021-06-29 csmc_mume_2020/paper/JCMS_2021/paper.tex
Add descr of Mel spectrogram

We then computed the Mel spectrogram of the combination to be the features input to our models. We generated the Mel spectrogram using an FFT hop length of 2048 samples (the window of each FFT was $46$ms long), and a number of Mel bins equal to 128. Therefore, the Mel features fed to the model were matrices of size $128\times 345$. We used the Librosa package in Python to compute the features; more details on the exact computations can be found in \cite{mcfee15}. The choice of the hop length was made by doing a compromise between the amount of information extracted by each FFT window, and the ability to capture temporal changes in the sound.

@@

In order to test our models for orchestration, we used 15 targets from the Orchidea distribution. These targets represent a variety of signal types but are mostly static, in the sense that the harmonic average across time is a good representation of the sample. Some of the targets were made of instrumental samples: a sum of oboe and bassoon notes, single bassoon and bass clarinet notes, two multiphonics of bassoon and two symphonic chords. Other targets were recordings that were not instrumental: bell sounds, car horn, gong, screaming voice, wind harp, the attack of a brass instrument, and the recording of a boat docking.

@@

Finally, the OrchideaSOL dataset could replace TinySOL as the dataset used. OrchideaSOL could improve the system by adding extended playing techniques to the data, which can allow noisier targets to be better orchestrated. OrchideaSOL contains 13,265 samples from 14 instruments, almost ten times as many samples as TinySOL~\cite{Cella2020b}. This would greatly increase the number of classes, and therefore we would need to train the models on more samples and possibly even use deeper models.

>>>>

We then computed the Mel spectrogram of the combination to be the features input to our models. We generated the Mel spectrogram using an FFT hop length of 2048 samples (the window of each FFT was $46$ms long), and a number of Mel bins equal to 128. Therefore, the Mel features fed to the model were matrices of size $128\times 345$. We used the Librosa package in Python to compute the features; more details on the exact computations can be found in \cite{mcfee15}. The choice of the hop length is a compromise between the amount of information extracted by each FFT window, and the ability to capture temporal changes in the sound.

@@

In order to test our models for orchestration, we used 15 targets from the Orchidea distribution. These targets represent a variety of signal types but are mostly static, meaning they do not have significant harmonic change over time. Some of the targets were made of instrumental samples: a sum of oboe and bassoon notes, single bassoon and bass clarinet notes, two multiphonics of bassoon and two symphonic chords. Other targets were recordings that were not instrumental: bell sounds, car horn, gong, screaming voice, wind harp, the attack of a brass instrument, and the recording of a boat docking.

@@

Finally, the OrchideaSOL dataset could replace TinySOL as the dataset used. OrchideaSOL could improve the system by adding extended playing techniques to the data, which can allow noisier targets to be better orchestrated. OrchideaSOL contains 13,265 samples from 14 instruments, almost ten times as many samples as TinySOL~\cite{Cella2020b}. This would greatly increase the number of classes, and therefore the models would need to be trained on more samples and the number of layers in the models may need to increase.
